---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Eric Stone"
date: "3.2.24"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(skimr)
```

```{r load-data, message = FALSE, eval = TRUE}
# Remove eval = FALSE or set it to TRUE once data is ready to be loaded
uoe_art <- read_csv("data/uoe-art.csv")
```

### Exercise 9

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, date)
```

### Exercise 10

> Fill in the blanks in to implement the data wrangling we described above. Note that this approach will result in some warnings when you run the code, and that’s OK! Read the warnings, and explain what they mean, and why we are ok with leaving them in given that our objective is to just capture year where it’s convenient to do so.


```{r cleaning date, error = TRUE}
uoe_art_cleandate <- uoe_art %>%
  mutate(date = as.numeric(str_remove_all(date, "[^0-9]")))
```

I believe the warnings are saying that not all of the pieces have titles and dates to be separated. That's okay -- we just want to get rid of the dates from those that have them.

### Exercise 11

> Print out a summary of the data frame using the skim() function. How many pieces have artist info missing? How many have year info missing?

```{r summary, error = TRUE}
library(skimr)
skim_data <- skim(uoe_art_cleandate)
n_missing_artists <- skim_data %>% 
  filter(skim_variable == "artist") %>% 
  pull(n_missing)
print(paste("Number of missing artists:", n_missing_artists))
n_missing_year <- skim_data %>% 
  filter(skim_variable == "year") %>% 
  pull(n_missing)
print(paste("Number of missing year:", n_missing_year))
```

There are `r n_missing_artists` missing artists and `r n_missing_year` years.

I'm not sure if this is what you had in mind with in-line code, but I found the print command from Lab 3, and chat reminded me of the pull command (which you likely told me about already). So this seems to work.  


115 have artist missing. 
1568 have year missing.

### Exercise 12

> Make a histogram of years. Use a reasonable binwidth. Do you see anything out of the ordinary?

```{r histogram for year, error = TRUE}
ggplot(data = uoe_art_cleandate, aes(x = year)) +
  geom_histogram(binwidth = 20.0)
```

You were right. A bin width of .2 wasn't enough. 

```{r frequency table for year, error = TRUE}
frequency_table <- uoe_art_cleandate %>%
  count(year) %>%
  arrange(desc(year))
print(frequency_table, n=6000)
```

 There's a "2" for year.

### Exercise 13

> Find which piece has the out of the ordinary year and go to its page on the art collection website to find the correct year for it. Can you tell why our code didn’t capture the correct year information? Correct the error in the data frame and visualize the data again.

It's Death Mask, by H. Dempshall.

On the website, it reads: Death Mask (2) (1964) 

Evidently, when reading in the information, it read the (2) as the date, not 1964.


> Hint: You’ll want to use mutate() and if_else() or case_when() to implement the correction.


```{r correcting year, error = TRUE}
uoe_art_cleanyear <- uoe_art_cleandate %>%
  mutate (newyear = case_when(
    year == 2 ~ 1964,
    TRUE ~ year 
  )) 
ggplot(data = uoe_art_cleanyear, aes(x = newyear)) +
  geom_histogram(binwidth = 20.0)
``` 


### Exercise 14

> Who is the most commonly featured artist in the collection? Do you know them? Any guess as to why the university has so many pieces from them?


```{r frequency table for artist, error = TRUE}
frequency_table_artist <- uoe_art_cleanyear %>%
  count(artist) %>%
  arrange(desc(n))
print(frequency_table_artist)
```

Emma Gillies. Nope, never heard of her, but that doesn't mean much. According to google, the University of Edinburgh has a special collection of her work. 

### Exercise 15

> Final question! How many art pieces have the word “child” in their title? See if you can figure it out, and ask for help if not.

```{r child in title, error = TRUE}
uoe_art_cleanyear_child <- uoe_art_cleanyear %>%
   mutate (child = case_when(
    str_detect(title, regex("Child", ignore_case = TRUE)) ~ 1,
    TRUE ~ 0 
  )) 
```

```{r frequency table for child in table, error = TRUE}
frequency_table_child <- uoe_art_cleanyear_child %>%
  count(child) %>%
  arrange(desc(child))
print(frequency_table_child)
```

Child (or some version thereof) appears to show up in 11 titles. Note I didn't fully follow your hint, but this approach seemed to work fine. 



